On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-26 docs/mvfits_paper/mvf.tex
misc updates

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  %
  Models of black hole properties play an important role in the ongoing direct detection of gravitational waves from black hole binaries.
  %
  In particular, model based gravitational wave detection, and subsequent estimation of source parameters are supported by the low level modeling of information related to perturbed Kerr black holes.
  %
  Here, we summarize recent methods and models for the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
  %
  Towards the construction of these models, two algorithms are presented.
  %
  A greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method are presented for the automated modeling of polynomial and rational functions respectively.
  %
  GMVR is a quasi-linear numerical method for interpolating rational functions. It therefore represents a solution to the problem of Runge's phenomenon.
	%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

During this period, a few to dozens of \bbh{} signals are likely to be detected. \cite{Abbott:2016nhf}.

@@

This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where only $n=0$ is explicitly considered.

@@

The consequences of this choice, in particular mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,London:2018gaq}.

@@

  g_j = \sum_{k=0}^{R+V+1} \, z_{k} \, \psi_k(\vec{x}_j) \;,

@@

Neither currently performs cross-validation, given sufficiently dense training data.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  %
  Models of black hole properties play an important role in the ongoing direct detection of gravitational waves from black hole binaries.
  %
  In particular, model based gravitational wave detection, and subsequent estimation of source parameters are supported by the low level modeling of information related to perturbed Kerr black holes.
  %
  Here, we summarize recent methods and models for the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
  %
  Towards the construction of these models, two algorithms are presented.
  %
  A greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method are presented for the automated modeling of polynomial and rational functions respectively.
  %
  GMVR is a quasi-linear numerical method for interpolating rational functions. It therefore represents a solution to Runge's phenomenon.
	%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

During this period, a few to dozens of \bbh{} signals are likely to be detected \cite{Abbott:2016nhf}.

@@

This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where only $n=0$ is explicitly considered, and ${_{-2}}Y_{\ell m}$ are the spins weighted -2 spherical harmonics.

@@

Only where $\jf \cw\lmn=0$ does $_{-2}S\lmn( 0,\theta,\phi) = {_{-2}}Y_{\ell m}\theta,\phi)$, which makes equating the spherical and spheroidal harmonics approximate at best for general values of $\jf \cw\lmn$.
The consequences of that choice, in particular the mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,London:2018gaq}.

@@

  g_j = \sum_{k=0}^{R+V} \, z_{k} \, \psi_k(\vec{x}_j) \;,

@@

If given sufficiently dense training data, neither currently performs cross-validation.
